Analysing Constraint Grammars with a SAT-solver

### 2015-10-25 paper/lrec/problem_desc.tex
merging two paragraphs; remove the unrelated related work

%In addition to analysing the whole grammar,
%Our method can be used to
%check individual rules. For instance,
We can also ask the tool to
generate example sentences that trigger rule(s) $R$ but not rule(s) $R'$. 
This can help the grammar writer to see
if they have implemented the rules in the intended way.

All of this requires a {\em semantic} rather than a {\em syntactic} analysis.

@@

In addition, there is a large body of research on automatically inducing rules, e.g. \cite{inducing_cg1996,lindberg_eineborg98ilp}.
%, \cite{lager01transformation}, \cite{asfrent14} 
However, since our work is aimed to aid the process of hand-crafting rules, we omit those works from our discussion.

>>>>

While rule-internal conflicts can be detected by simpler means, taking
care of rule interaction requires a {\em semantic} rather than a {\em syntactic} analysis.
%In addition to analysing the whole grammar,
%Our method can be used to
%check individual rules. For instance,
We can also ask the tool to
generate example sentences that trigger rule(s) $R$ but not rule(s) $R'$. 
This can help the grammar writer to see
if they have implemented the rules in the intended way.

@@

% In addition, there is a large body of research on automatically inducing rules, e.g. \cite{inducing_cg1996,lindberg_eineborg98ilp}.
% %, \cite{lager01transformation}, \cite{asfrent14} 
% However, since our work is aimed to aid the process of hand-crafting rules, we omit those works from our discussion.
